Using Mean-Squared-Error in Log-Transformed Domain to Evaluate Speckle Filters.

### 2013-03-01 paper_dev/article_vch.tex
201303_Mar01

%\author{Thanh-Hai Le, Ian McLoughlin}
\author{Thanh-Hai~Le,
        Ian~McLoughlin,~\IEEEmembership{Senior Member,~IEEE}, 
	Brian~Quang-Huy~Nguyen,
	Nicholas~Chan-Hua~Vun%
	%Ken-Yoong~Lee, 
	%and Timo~Brestchneider % <-this % stops a space
\thanks{Thanh-Hai~Le, Brian~Quang-Huy~Nguyen, Nicholas~Chan-Hua~Vun, and Ian~McLoughlin are with School of Computer Engineering, 
Nanyang Technological University, Singapore,}% <-this % stops a space
%\thanks{Ken-Yoong Lee and Timo Brestchneider are with EADS InnovationWorks Singapore.}% <-this % stops a space
\thanks{Manuscript received ?, 2012; revised ?.}}

@@

Logarithmic transformation has the potential to convert 
	the multiplicative and heteroskedastic statistical distribution of SAR speckle noise into 
	a simpler additive and homoskedastic distribution model.
From this homoskedastic model, within the log-transformed domain, 
	a few consistent measures of distance emerge.
With these, subtractive differences become consistent and predictable. 
We show, through experiments and analysis, that 
	the familiar mean squared error (MSE) criteria can reliably serve 
		as a single unifying performance indicator to evaluate SAR speckle filters. 
In homogeneous areas, we determine a mathematical relationship that links the variance of log-transformed SAR data with the canonical Equivalent-Number-of-Looks index.
For heterogenous scenes, the standard residual-based bias evaluation, also in the log-transformed domain, 
	is shown to be equivalent to the ratio-based radiometric preservation criteria usually assessed in the original domain. 
Through experiments, and analysis, we show that lower MSE suggests better feature detection and classification ability, an important requirement for subsequent post-filtering steps in practical SAR data processing.
Combined, we propose and describe the use of log-transformed MSE to evaluate SAR speckle filters.

@@

The nature of SAR speckle is that
	it is stochastic even when the underlying radiometry is constant, 
	and when there are spatial variation of this radiometry, not only its expected value changes, but so does its heteroskedastic variance.
Nevertheless, statistical models have been developed to derive the underlying back-scattering coefficient ($\sigma$) from measured SAR data. 
Then speckle filters are, by and large, estimators that attempt to determine this unknown coefficient from observable SAR data.

SAR speckle-filtering can be, and has been, positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. 
The stages in this statistical framework consist of statistical modelling, estimator development and evaluating the estimators' performance. 
Estimators are typically evaluated based on the bias and variance properties of their estimates; 
	with lower bias and / or lower variance (hence lower MSE) being indicative of better accuracy.
Ideally, estimator evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
Also, due to the stochastic nature of SAR processing, as well as simulating process, 
	statistical summaries of repeatedly simulated experiments are normally preferred to single-run results.

Our survey of SAR speckle filter research, however, indicates 
	a different picture from the standard practice of the statistical framework, 
	specifically, in the stage of performance evaluation. 
Due to the multiplicative and heteroskedastic nature of speckle noise, 
	bias and variance evaluation may not be the most useful measures. 
Thus, the standard evaluation metric of mean-squared-error is not easily applicable,
	so alternative evaluation criteria are proposed.
In fact, a survey of relevant literature fails to reveal 
	a single universally agreed quantitative metric for the performance of speckle filters.

The common theme is that each newly proposed speckle filter tends to be published along with a methodology for evaluating its performance.
Many papers lack a comparative basis beyond simple visual qualititave comparision on a few image scenes. 
While such visual comparison is useful, as an evaluative methodology, it regretably lacks scientific objectivity. 
Some papers do present quantitative measurements, 
	however  due to the lack of a standardized performance criteria, 
	the evaluation metrics can change significantly from one paper to the next.

In this paper, we propose and evaluate the use of MSE in the homoskedastic log-transformed domain to evaluate speckle filters. 
The paper is structured as follows.
Section \ref{sec:lit_review} briefly surveys related work in the published literature, Section \ref{sec:log_transform} provides a brief discussion of the logarithmic transformation.
Section \ref{sec:eval_homo} then illustrates the use of variance (an MSE component) in the log-transformed domain to evaluate different filters' speckle suppression power over homogeneous areas.
Section \ref{sec:eval_hetero} describes the use of the same MSE to evaluate the performance of speckle filters in heterogeneous areas.
Section \ref{sec:practical_conjecture} hypothesises the use of residual MSE in the log-transformed domain 
	as a criteria for choosing the most suitable speckle filter for a given satellite-captured SAR image.
%And the last section provides our discussion together with our concluding remarks.
Finally, Section \ref{sec:discussion} discusses the findings and presents concluding remarks.

@@

%Addressing this issue, 
%There have been a few published articles dedicated to the topic of evaluating speckle filters.
%However, our survey of SAR speckle filtering research indicates 
%	the lack of a single universally-agreed quantitative metric to evaluate speckle filters.
%In this section, we briefly review published work 
%	related to the topic of evaluating SAR speckle filters.	
It is customary to divide the evaluation of speckle filters into their performance across the two classes of 
	homogeneous and heterogeneous regions.
Across homogeneous areas,
	speckle filters are expected to estimate with negligible radiometric bias.
Thus evaluating speckle filters over homogeneous areas has traditionally been focused on evaluating the variation of the estimators' output (i.e. the speckle suppression power).
By contrast, the methodologies used to evaluate speckle filters over heterogeneous areas are much more complex, due in part to the following difficulties.
The first is that of determining an absolute ground-truth against which quantitative criteria can be measured.
The second challenge is then to define a quantifiable metric allowing the performance of different speckle filters to be measured and compared.
%IVMIn this section, various published work in evaluating SAR speckle filters are reviewed.

In general, any metric to evaluate speckle filters should be relevant to the normal usage of such filters. Furthermore, its application in a SAR processing framework should allow an improvement in the measurement, detection or classification of the underlying radiometric features.
%As shown in the subsequent section, 
%	one can choose to work in the original domain of SAR data where the speckle is multiplicative and heteroskedastic, or
%	logarithmic transformation can be utilized to convert SAR data into a simpler additive and homoskedastic model.
As shown in the subsequent sections, by applying log-transformation, 
	this overall requirement of speckle filtering can be broken down into two smaller requirements.
On the one hand, speckle filters should preserve the underlying radiometric signal (namely the radiometric preservation requirement).
On the other hand, they should reduce the variation of the additive noise (i.e. speckle suppression power).
These requirements can be measured and evaluated by determining, also in the log-transformed domain, the bias and variance error of the output.
The MSE evaluation is a combined evaluation of bias and variance error, and is therefore capable of evaluating the general requirement of speckle filtering.
%Combined the overall general requirement of speckle filters can be evaluated using the traditional Mean-Squared-Error.

@@

One metric that can be used to detect radiometric distortion is the ratio between the estimated and the original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
A somewhat similar metric is used in \cite{Wang_2005_MIPR} as $r_w = (X_{est} - X_{org} )/ X_{org}$.
In the log-transformed domain, the equivalent index for evaluation would, of course, be a simple substraction.
In other words, it is evident that the bias evaluation in the log-transformed domain can be used to evaluate the radiometric preservation requirement of speckle filters.

Specifically for homogeneous scenes, Shi et al. \cite{Shi_IGARSS_1994} found that 
	in the original domain the ``standard'' filters (boxcar, Lee\cite{Lee_PAMI_1980}, Kuan \cite{Kuan_1985_PAMI}, Frost\cite{Frost_PAMI_1982}, MAP\cite{Lopes_IGARSS_1990}) and their enhanced versions \cite{Lopes_TGRS_1990} can achieve negligible bias. 
In this paper, we will also show that all of these standard filters 
	not only preserves the expected radiometric values, 
	but in the log-transformed domain they also preserve a few subtractive and consistent measures of distance.

Several metrics have been developed to evaluate speckle suppression power.
The most common measure is the Equivalent Number of Looks (ENL) index 
$ENL=avg(I)^2/var(I)$
that was proposed by Lee \cite{Lee_1981_CGIP}.
Another very similar metric is the ratio of mean to standard deviation, $R=avg(I)/std(I)$ \cite{Gagnon_SPIEProc_1997} 
In Section \ref{sec:eval_homo}, it will be shown that, for homogeneous areas, ENL is related to variance in the log-transformed domain.
%However, since Lopes' underlying assumption of the scene variation may not be applicable in a designed test pattern, we do not consider the index further in these experiments.
Subsequently, we propose the use of log-variance to evaluate the noise suppression power of speckle filters which is the primary criteria to evaluate speckle filters over homogeneous area.
%Combined, in homogeneous area, we show that variance evaluation in log-transformed domain, 
%	which is a component of MSE evaluation, 
%	can be and practically has been used to evaluate speckle filters.
%Combined, we show that Mean Squared Error in log-transformed domain can be used to evaluate speckle filters not only in homogeneous areas but also in heterogeneous scenes.

Real-life and practical images, however, are not homogeneous.
Thus there are a few associated difficulties in evaluating speckle filters over heterogenous scenes.
%and there are many proposed methods of evaluating speckle filters in such areas. 
%It is here that the situation becomes less structured, and more `exciting' from a research perspective.
%and it is here that things gets a lot more exciting and unstructured to evaluate speckle filters in heterogenous area.
The first difficulty in evaluating speckle filters for heterogeneous scenes is to select the basis for comparision. 
It is trivially easy to estimate the underlying radiometric coefficient if an area is known to be homogeneous
However, without simulation or access to solid ground-truth, it is practically impossible to do so for real-life images (hence, the need for speckle filters estimation).

Without ground truth, one way to evaluate radiometric preservation of filters is to compute the ratio image, mentioned above. 
Under a multiplicative model, the ratio image is expected to comprise the noise being removed, (i.e. it should be completely random). 
Being random, this should display as little ``visible'' structure as possible. 
%Also its histogram and PDF are expected to match the noise characteristics in the original image as closely as possible.
However, when displaying such images for visual evaluation, ratios that are smaller than unity are much harder to distinguish than those that are bigger \cite{Medeiros_2003_IJRS}, meaning that a purely visual analysis may be insufficient.
We therefore propose to adopt a log-transformed domain approach where multiplicative noise then resembles the familiar additive model.
The ratio image then becomes a simple subtraction image.
The evaluation methodology for such a proposal does not differ, but now the residual image is additive and linear and thus more natural to display and evaluate visually (see \ref{sec:schema_log_images}).

Another way to evaluate speckle filters is by assessing the feature preservation characteristics of the original noised data and those of the filtered image. 
When there is no ground-truth given, the feature are estimated in both the original noised and the filtered images.
Evaluation would then determine how closely related the two feature maps are. 
Various methods may be applied to extract features; some that have been used are the Hough Transform \cite{Medeiros_2003_IJRS}, Robert gradient edge detector \cite{Gagnon_SPIEProc_1997} or edge map \cite{Frost_PAMI_1982}.
While significant effort has been spent on these evaluations, serious doubts remain concerning the precision of this methodology.
This is because feature extraction algorithms are only approximations 
	whose accuracy is 
		not only dependent upon the characteristics of the original image 
		but also heavily reliant on the inherent noise.
Unfortunately, speckle filters invariably alter the noise characteristics.
Thus, without a clear understanding of these dependencies and no absolute ground truth, 
	using feature extraction algorithms to evaluate speckle filters would leave serious questions on how to interpret the results, especially its accuracy.
%is just too imprecise for us.

@@

Even with known ground-truth, evaluating metrics need to be defined for quantitative measurements.
This is the second difficulty in evaluating speckle filters for heterogenous scenes.
Under conditions of heterogeneity, the standard speckle filters still introduce radiometric loss, normally at local or regional levels.
In fact the common consensus is that a powerful speckle suppresion filter (for example the boxcar filter) is likely to perform poorly in terms of preserving underlying radiometric differences (such as causing excessive blurring), and vice versa. 
%One can relatively easily satisfy one of these criteria, but not easily satisfy both.
%Thus, the second difficulty in evaluating speckle filters for heterogeneous scene is to find a single valid metrics to measure the performance of speckle filters.

@@

In this paper, homoskedastic property is shown to be available after logarithmic transformation of SAR data.
As the important Gauss Markov theorem becomes applicable again, 
	the use of MSE is shown to be relevant again in evaluating statistical estimators (i.e. speckle filters).
Initial intitution suggests that each components of the MSE measure, 
	namely bias and variance evaluation, can be mapped into 
	the requirements of radiometric preservation and speckle suppression for speckle filters.
Before the details of our evaluation methodology is discussed and presented, 
	Section \ref{sec:log_transform} provides a brief discussion on logarithmic transformation for SAR images.

@@

In the first portion of this section,
    the SAR speckle model in the original domain is shown to be multiplicative and heteroskedastic.
Next the impacts of heteroskedasticity on speckle filtering is discussed.
Then logarithmic transformation is shown to convert original speckle data into an homoskedastic model, where the noise is not only additive, but also independent of the underlying radiometric signal.
From the consistent and additive noise in log-transformed domain,
    the consistent measures of dispersion ($ln(I)-ln(avg(I))$), contrast ($ln(I_1)-ln(I_2)$ and variance ($var(ln(I))$) are described.

@@

Assuming the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}, then the real part $A_r$ as well as the imaginary part $A_i$ of the observed SAR signal $A$ can be considered as random variables from uncorrelated Gaussian distributed stochastic processes with zero means and indentical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}. Their probability density function (pdf) is given as:

@@

It then can be proved that the measurable amplitude $A=\sqrt{A_r^2+A_i^2}$ is a random variable of Rayleigh distribution and consequently intensity $I=A^2=(A_r^2+A_i^2)$ is a random variable of negative exponential distributed random process.

@@

%For about 30 years, speckle filtering has been an active research area, with new methods being introduced steadily. 
%That is because: 
Even though the statistical model within individual resolution cells is well established, the applicability of its models is restricted to homogenous areas. 
Practical images, however, are heterogenous. Crucially it is this spatial variation that is of high interest. This fact gives rise to a question that seemed obvious: how to label an analysis area as being heterogenous and subsequently what to do in the case of heterogeneity.

Various statistical models for heterogenous areas have been proposed (see \cite{Touzi_2002_TGRS} for a detailed review). 
Unfortunately, while most of the models highlight the multiplcative nature of sub-pixel or homogenous original SAR data, in extending the models to heterogenous images, virtually none have noted that spatial varition also gives rise to the heteroskedasticity phenomena. 
Heteroskedasticity, as explained in the previous section, is defined as the dependence of conditional expected variance of original SAR data on the conditional expectation of its mean, or equivalently its underlying back-scattering coefficient $(\sigma)$.
It is believed that this heteroskedasticity give rise to serious negative impacts at various stages of speckle-filtering.

@@

Heteroskedasticity also poses numerous challenges in designing and evaluating an efficient estimator. 
Heteroskedasticity directly violates Gauss-Markov theorem's homoskedastic assumption. 
Thus it renders the efficiency of any naive Ordinary Least Square estimator \cite{Furno_1991_JStatCompSimul}, together with the normal Mean Squared Error evaluation criteria in serious doubt. 
If the variance is known \textit{a priori}, it has been proven, that a weighted mean estimator is the best linear unbiased estimator. 
Interestingly, as noted by Lopes \cite{Lopes_TGRS_1990}, most known common successful adaptive filters \cite{Lee_PAMI_1980} \cite{Kuan_1985_PAMI} \cite{Frost_PAMI_1982} does make use of weighted mean estimators. 
The caveat however is that in SAR speckle filtering, variance is not known a priori. 
And eventhough variance can be estimated from observable values, as the vicious circle goes, estimating the variance is as good as estimating the underlying coefficient $\sigma$ itself.

@@

Last but certainly not least, is the bad impact of heteroskedastic on SAR image interpretation. 
Most of the task to be carried out in intepreting SAR images almost certainly involves target detection, target segmentation and/or target classification. 
Each of these tasks require good similarity or discriminant functions. 
Foundational to these is the need of a consistent measures of distance. 
Unfortunately, by definition heteroskedasticity leads to inconsistent measures of distance. 
This inconsistent measure of distance coupled with the failure of the ordinary least square regression methods are
 believed to cause a large class of artificial neural networks as well as a number of other computational intelligence methods for SAR classification to underperform.

@@

In this paper, we propose using a base-2 logarithmic transformtion of orignal SAR data. Base-2 is chosen for implementation reasons since it can be computed faster than either natural or decimal logarithms, and yet maintains an ability to transform heterskedactic speckle into a homoskedastic relationship. Thus the original variables become:

@@

Bearing the relationship among the random variables in mind, it is then trivial to give the probability distribution of these log-transformed variables as follows:

@@

The equations above also highlight the relationships among random variables in the log-transformed domain. 
Two conclusions become evident from these formula. 
Firstly, in the log-transformed domain, working on either amplitude or intensity will tend to give identical results. 
Secondly, the effects of converting the multiplicative nature to an additive nature through logarithmic transformation is clearly manifested. 
Table \ref{tbl:sar_log_domain_avg_var} confirms the condition of homoskedasticity,  defined as the independence of the conditional expected variance on the conditional expectation of the mean.

This result is consistent with finding by Arsenault \cite{Arsenault_JOptSocAm_1976}. The main difference would be the use of base-2 logarithm which is prefered here for faster computation.

>>>>

%\author{Thanh-Hai Le, Ian McLoughlin}
\author{Thanh-Hai~Le,
        Ian~McLoughlin, 
	    Quang-Huy~Nguyen,
	    Chan-Hua~Vun%
	%Ken-Yoong~Lee, 
	%and Timo~Brestchneider % <-this % stops a space
}
\thanks{Thanh-Hai~Le, Quang-Huy~Nguyen and Chan-Hua~Vun, are with School of Computer Engineering, 
Nanyang Technological University, Singapore. Ian~McLoughlin is with School of Information Science and Technology,
University of Science and Technology of China.
}% <-this % stops a space
\thanks{The authors wish to thank Dr. Ken-Yoong Lee and Dr. Timo Brestchneider of EADS InnovationWorks Singapore for 
	initial discussions and for providing RADARSAT2 images used in this paper. }% <-this % stops a space
\thanks{Manuscript received ?, 2012; revised ?.}}

@@

Logarithmic transformation has the potential to convert 
	the multiplicative and heteroskedastic statistical distribution of SAR speckle noise into 
	a simpler additive and homoskedastic distribution model.
From this homoskedastic model, within the log-transformed domain, 
	a few consistent measures of distance emerge.
With these, subtractive differences become consistent and predictable. 
We show, through experiments and analysis, that 
	the familiar mean squared error (MSE) criteria can reliably serve 
	as a single unifying performance indicator to evaluate SAR speckle filters. 
In homogeneous areas, we establish a mathematical relationship that links the variance of 
	log-transformed SAR data with the canonical Equivalent-Number-of-Looks index.
For heterogenous scenes, the standard residual-based bias evaluation, also in the log-transformed domain, 
	is shown to be equivalent to the ratio-based radiometric preservation criteria that is usually assessed in the 
	original domain. 
Through experiments as well as analysis, we show that lower MSE suggests better feature detection and classification
	ability, which is an important requirement for subsequent post-filtering steps in practical SAR data processing.
In this paper, we hence propose and describe the combined use of log-transformed and MSE to evaluate SAR speckle 
	filters.

@@

The nature of SAR speckle is that
	it is stochastic even when the underlying radiometry is constant, 
	and when there are spatial variation of this radiometry, not only its expected value changes, but so does its heteroskedastic variance.
Nevertheless, statistical models have been developed to derive the underlying back-scattering coefficient ($\sigma$) from measured SAR data. 
As such, speckle filters are, by and large, estimators that attempt to determine this unknown coefficient from observable SAR data.

SAR speckle-filtering can be, and has been, positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. 
The stages in this statistical framework consist of statistical modelling, estimator development and evaluation of the estimators' performance. 
Estimators are typically evaluated based on the bias and variance properties of their estimates; 
	with lower bias and / or lower variance (hence lower MSE) indicating better accuracy.
Ideally, estimator evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
In addition, due to the stochastic nature of SAR processing, as well as the simulating process, 
	statistical summaries of repeatedly simulated experiments are normally preferred to single-run results.

Our survey of SAR speckle filter research, however, indicates 
	a different picture from the standard practice of the statistical framework, 
	specifically, in the stage of performance evaluation. 
Due to the multiplicative and heteroskedastic nature of speckle noise, 
	bias and variance evaluation may not be the most useful measures. 
Thus, the standard evaluation metric of mean-squared-error is not easily applicable,
	prompting alternative evaluation criteria to be proposed.
In fact, a survey of relevant literature fails to reveal 
	a single universally agreed quantitative metric for the performance of speckle filters.

Most commonly, each newly proposed speckle filter tends to be published along with its own methodology for evaluating its 
	performance. 
As such, many papers lack a comparative basis beyond simple visual qualititave comparision on a few image scenes. 
While such visual comparison is useful, as an evaluative methodology, it regretably lacks scientific objectivity. 
Some papers do present quantitative measurements. 
However, due to the lack of a standardized performance criteria, 
	the evaluation metrics can change significantly from one paper to the next.

In this paper, we propose and validate the use of MSE in the homoskedastic log-transformed domain to evaluate speckle filters. 
The paper is structured as follows.
Section \ref{sec:lit_review} briefly surveys related work in the published literature, 
Section \ref{sec:log_transform} provides a brief discussion of the logarithmic transformation.
Section \ref{sec:eval_homo} then illustrates the use of variance (an MSE component) in the log-transformed domain to 
	evaluate different filters' speckle suppression power over homogeneous areas.
Section \ref{sec:eval_hetero} describes the use of the same MSE to evaluate the performance of speckle filters in heterogeneous areas.
Section \ref{sec:practical_conjecture} hypothesizes the use of residual MSE in the log-transformed domain 
	as a criteria for choosing the most suitable speckle filter for a given satellite-captured SAR image.
%And the last section provides our discussion together with our concluding remarks.
Finally, Section \ref{sec:discussion} discusses the findings and presents concluding remarks.

@@

%Addressing this issue, 
%There have been a few published articles dedicated to the topic of evaluating speckle filters.
%However, our survey of SAR speckle filtering research indicates 
%	the lack of a single universally-agreed quantitative metric to evaluate speckle filters.
%In this section, we briefly review published work 
%	related to the topic of evaluating SAR speckle filters.	
It is customary to divide the performance evaluation of speckle filters across the two classes of 
	homogeneous and heterogeneous regions.
Across homogeneous areas, speckle filters are expected to estimate with negligible radiometric bias.
As such, evaluating speckle filters over homogeneous areas has traditionally been focused on evaluating the variation of the estimators'
	output (i.e. the speckle suppression power).
In contrast, the methodologies used to evaluate speckle filters over heterogeneous areas are much more complex, 
	due in part to the following difficulties.
The first is that of determining an absolute ground-truth against which quantitative criteria can be measured.
The second challenge is to then define a quantifiable metric that allows the performance of different speckle filters 
	to be measured and compared.
%IVMIn this section, various published work in evaluating SAR speckle filters are reviewed.

In general, any metric to evaluate speckle filters should be relevant to the normal usage of such filters.
Furthermore, its application in a SAR processing framework should enable an improvement in the measurement, 
	detection or classification of the underlying radiometric features.
%As shown in the subsequent section, 
%	one can choose to work in the original domain of SAR data where the speckle is multiplicative and heteroskedastic, or
%	logarithmic transformation can be utilized to convert SAR data into a simpler additive and homoskedastic model.
As shown in the subsequent sections, by applying log-transformation, 
	this overall requirement of speckle filtering can be further broken down into two smaller requirements.
On the one hand, speckle filters should preserve the underlying radiometric signal (namely the radiometric 
	preservation requirement).
On the other hand, they should reduce the variation of the additive noise (i.e. speckle suppression power).
These requirements can be measured and evaluated by determining, also in the log-transformed domain, the bias 
	and variance error of the output.
As the MSE evaluation is a combined evaluation of bias and variance error, it is therefore capable of evaluating 
	the general requirements of speckle filtering.
%Combined the overall general requirement of speckle filters can be evaluated using the traditional Mean-Squared-Error.

@@

One metric that can be used to detect radiometric distortion is the ratio between the estimated and the 
	original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
A somewhat similar metric is used in \cite{Wang_2005_MIPR} as $r_w = (X_{est} - X_{org} )/ X_{org}$.
In the log-transformed domain, the equivalent index for evaluation could be performed by a simple substraction.
In other words, it is clear that the bias evaluation in the log-transformed domain 
	can be used to similarily evaluate the radiometric preservation requirement of speckle filters.

Specifically for homogeneous scenes, Shi et al. \cite{Shi_IGARSS_1994} found that 
	in the original domain the ``standard'' filters (boxcar, Lee\cite{Lee_PAMI_1980}, 
	Kuan \cite{Kuan_1985_PAMI}, Frost\cite{Frost_PAMI_1982}, 
	MAP\cite{Lopes_IGARSS_1990}) and their enhanced versions \cite{Lopes_TGRS_1990} can achieve negligible bias. 
In this paper, we will also show that all of these standard filters 
	not only preserves the expected radiometric values in the log-transformed domain,
	they also preserve a number of subtractive and consistent measures of distance.

Several metrics have been developed to evaluate speckle suppression power.
The most common measure is the Equivalent Number of Looks (ENL) index 
$ENL=avg(I)^2/var(I)$
that was proposed by Lee \cite{Lee_1981_CGIP}.
Another very similar metric is the ratio of mean to standard deviation, $R=avg(I)/std(I)$ \cite{Gagnon_SPIEProc_1997} 
In Section \ref{sec:eval_homo}, it will be shown that, for homogeneous areas, ENL is related to variance in the 
	log-transformed domain.
%However, since Lopes' underlying assumption of the scene variation may not be applicable in a designed test pattern, we do not consider the index further in these experiments.
Subsequently, we propose the use of log-variance to evaluate the noise suppression power of speckle filters, 
	which is the primary criteria used to evaluate speckle filters over homogeneous area.
%Combined, in homogeneous area, we show that variance evaluation in log-transformed domain, 
%	which is a component of MSE evaluation, 
%	can be and practically has been used to evaluate speckle filters.
%Combined, we show that Mean Squared Error in log-transformed domain can be used to evaluate speckle filters not only in homogeneous areas but also in heterogeneous scenes.

Real-life and practical images, however, are not homogeneous.
Thus there are a number of associated difficulties in evaluating speckle filters over heterogenous scenes.
%and there are many proposed methods of evaluating speckle filters in such areas. 
%It is here that the situation becomes less structured, and more `exciting' from a research perspective.
%and it is here that things gets a lot more exciting and unstructured to evaluate speckle filters in heterogenous area.
The first difficulty in evaluating speckle filters for heterogeneous scenes is to select the basis for comparision. 
It is trivially easy to estimate the underlying radiometric coefficient if an area is known to be homogeneous.
However, without simulation or access to solid ground-truth, it is practically impossible to do so for 
	real-life images (hence, the need for speckle filters estimation).

Without ground truth, one way to evaluate radiometric preservation of filters is to compute the ratio image 
	mentioned above. 
Under a multiplicative model, the ratio image is expected to comprise (???? comprise of data with ?)
	the noise being removed (i.e. it should be completely random). 
Being random, this should display as little ``visible'' structure as possible. 
%Also its histogram and PDF are expected to match the noise characteristics in the original image as closely as possible.
However, when displaying such images for visual evaluation, ratios that are smaller than unity are much 
harder to distinguish than those that are bigger \cite{Medeiros_2003_IJRS}, 
meaning that a purely visual analysis may be insufficient.
We therefore propose to adopt a log-transformed domain approach where multiplicative noise 
would then resemble the familiar additive model, and the ratio image would then become a simple subtraction image.
The evaluation methodology for such a proposal does not change, 
	but now the residual image is additive and linear, 
	and would be more natural to be displayed and evaluated visually (see \ref{sec:schema_log_images}).

Another way to evaluate speckle filters is by comparing the feature preservation characteristics 
of the original noised data and those of the filtered image. 
When there is no ground-truth given, the feature are estimated in both the original noised and the filtered images.
Evaluation would then determine how closely related the two feature maps are. 
Various methods may be applied to extract features; examples of those that have been used are the 
	Hough Transform \cite{Medeiros_2003_IJRS}, Robert gradient edge detector \cite{Gagnon_SPIEProc_1997} 
	and edge map \cite{Frost_PAMI_1982}.
While significant effort has been spent on these evaluations, serious doubts remain concerning the precision 
of these methodologies.
This is because feature extraction algorithms are only approximations,
	whose accuracy is not only dependent upon the characteristics of the original image 
		but also heavily affected by 
		%reliant on 
		the inherent noise.
Unfortunately, speckle filters invariably alter the noise characteristics.
Thus, without a clear understanding of these dependencies and no absolute ground truth, 
	using feature extraction algorithms to evaluate speckle filters would leave serious questions on 
	how to interpret the results, especially its accuracy.
%is just too imprecise for us.

@@

Even with known ground-truth, evaluating metrics need to be defined for quantitative measurements.
This is the second difficulty in evaluating speckle filters for heterogenous scenes.
Under the conditions of heterogeneity, the standard speckle filters still introduce radiometric loss, 
	normally at local or regional levels.
In fact, the common consensus is that a powerful speckle suppresion filter (for example the boxcar filter) 
	is likely to perform poorly in terms of preserving underlying radiometric differences 
	(such as causing excessive blurring), and vice versa. 
%One can relatively easily satisfy one of these criteria, but not easily satisfy both.
%Thus, the second difficulty in evaluating speckle filters for heterogeneous scene is to find a single valid metrics to measure the performance of speckle filters.

@@

In this paper, homoskedastic property is shown to be available after logarithmic transformation of SAR data.
As the important Gauss Markov theorem becomes applicable again, 
	the use of MSE is shown to be relevant again in evaluating statistical estimators (i.e. speckle filters).
Initial intitution (??? intuition?)
	suggests that each components of the MSE measure, 
	namely bias and variance evaluation, can be mapped into 
	the requirements of radiometric preservation and speckle suppression for speckle filters.
Before the details of our evaluation methodology is presented and discussed, 
	Section \ref{sec:log_transform} provides a brief discussion on logarithmic transformation for SAR images.

@@

In 
%the first portion of 
this section, the SAR speckle model in the original domain is first shown to be multiplicative and heteroskedastic.
The impacts of heteroskedasticity on speckle filtering is then discussed.
Logarithmic transformation is then shown to convert original speckle data into an homoskedastic model, 
	where the noise is not only additive, but also independent of the underlying radiometric signal.
From the consistent and additive noise in log-transformed domain,
    the consistent measures of dispersion ($ln(I)-ln(avg(I))$), contrast ($ln(I_1)-ln(I_2)$ and 
	variance ($var(ln(I))$) are described.

@@

Assuming the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}, the real part $A_r$ as well as 
the imaginary part $A_i$ of the observed SAR signal $A$ can then be considered as random variables from 
uncorrelated Gaussian distributed stochastic processes with zero means and 
% indentical ??? 
identical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}. Their probability density function (pdf) is given as:

@@

It can then be proved that the measurable amplitude $A=\sqrt{A_r^2+A_i^2}$ is a random variable of Rayleigh 
distribution and consequently the intensity $I=A^2=(A_r^2+A_i^2)$ is a random variable of negative exponential 
distributed random process.

@@

%For about 30 years, speckle filtering has been an active research area, with new methods being introduced steadily. 
%That is because: 
Even though the statistical model within individual resolution cells is well established, the applicability of its 
models is restricted to homogenous areas. 
Practical images, however, are heterogenous. Crucially it is this spatial variation that is of high interest. 
This fact gives rise to a question that seemed obvious: how to label an analysis area as being heterogenous and 
subsequently, what to do in the case of heterogeneity.

Various statistical models for heterogenous areas have been proposed (see \cite{Touzi_2002_TGRS} for a detailed 
review). Unfortunately, while most of the models highlight the multiplcative nature of sub-pixel or homogenous 
original SAR data, in extending the models to heterogenous images, virtually none have noted that spatial variation 
also gives rise to the heteroskedasticity phenomena. 
Heteroskedasticity, as explained in the previous section, is defined as the dependence of conditional expected 
variance of original SAR data on the conditional expectation of its mean, or equivalently its underlying 
back-scattering coefficient $(\sigma)$.
It is believed that this heteroskedasticity gives rise to serious negative impacts at various stages of 
speckle-filtering.

@@

Heteroskedasticity also poses numerous challenges in designing and evaluating an efficient estimator. 
Heteroskedasticity directly violates Gauss-Markov theorem's homoskedastic assumption. 
Thus it renders the efficiency of any naive Ordinary Least Square estimator \cite{Furno_1991_JStatCompSimul}, 
together with the normal Mean Squared Error evaluation criteria in serious doubt. 
If the variance is known \textit{a priori}, it has been proven that a weighted mean estimator is the 
best linear unbiased estimator. 
Interestingly, as noted by Lopes \cite{Lopes_TGRS_1990}, most known common successful adaptive 
filters \cite{Lee_PAMI_1980} \cite{Kuan_1985_PAMI} \cite{Frost_PAMI_1982} does make use of weighted mean estimators. 
However, the caveat is that in SAR speckle filtering, variance is not known \textit{a priori}. 
And even though variance can be estimated from observable values, as the vicious circle goes, 
estimating the variance is as good as estimating the underlying coefficient $\sigma$ itself.

@@

Last, but certainly not least is the bad impact of heteroskedastic on SAR image interpretation. 
Most of the task to be carried out in intepreting SAR images almost certainly involves target detection, 
target segmentation and/or target classification. 
Each of these tasks require good similarity or discriminant functions. 
Foundational to these is the need of a consistent measures of distance. 
Unfortunately, by definition, heteroskedasticity leads to inconsistent measures of distance. 
This inconsistent measure of distance, coupled with the failure of the ordinary least square regression methods, are
 believed to cause a large class of artificial neural networks as well as a number of other computational 
 intelligence methods for SAR classification to underperform.

@@

In this paper, we propose using a base-2 logarithmic transformtion of orignal SAR data. 
Base-2 is chosen for implementation reasons since it can be computed faster than either natural or 
decimal logarithms, and yet maintains the ability to transform heterskedactic speckle into a 
homoskedastic relationship. Thus the original variables become:

@@

Bearing the relationship among the random variables in mind, it is then trivial to 
show that the probability distribution of these log-transformed variables are related as follows:

@@

The equations above also highlight the relationships among random variables in the log-transformed domain. 
Two conclusions become evident from these formulae. 
Firstly, in the log-transformed domain, working on either amplitude or intensity will tend to give identical results. 
Secondly, the effects of converting the multiplicative nature to an additive nature through logarithmic transformation
is clearly manifested. 
Table \ref{tbl:sar_log_domain_avg_var} confirms the condition of homoskedasticity,  
defined as the independence of the conditional expected variance on the conditional expectation of the mean.

This result is consistent with finding by Arsenault \cite{Arsenault_JOptSocAm_1976}. 
The main difference would be the use of base-2 logarithm which is preferred here for more efficient computation.

Table \ref{tbl:sar_variables_properties} summarizes the discussion so far. 
It can be seen that while the original data, especially intensity values, should be preferred for 
multi-look processing, the log-transformed domain with its homoskedastic distribution offers consistent measures of 
dispersion and contrast. 
Thus log transformation is shown here to be a homomorphic transformation, allowing one to apply traditional linear, 
additive, least squared error regression signal processing (including wavelets) and computational 
(including artificial neural network) techniques on SAR data.
